SafeNet: A European database of plant-pollinator interactions

### 2024-03-07 Manuscript/Ms.qmd
Edits

---
title: "SafeNet: A European database of plant-pollinator interactions"
format:
  pdf:
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
        \usepackage{caption}
        \captionsetup[figure]{labelformat=empty}

@@

@@

# Introduction

@@

# Methods

@@

#Data structure

EXPLAIN!!!

@@

#Create variables
vars = colnames(safenet_database)
#Create table
d = tibble(Variable = vars)

#Add descriptor
my_tibble = d %>%
  mutate(Description = case_when(
    Variable == "Study_id" ~ "Identifier of the study",
    Variable == "Network_id" ~ "Identifier of a site sampled within a study",
    Variable == "Sampling_method" ~ "Type of plant-pollinator sampling",
    Variable == "Authors_habitat" ~ "Type of habitat as described by the authors",
    Variable == "SafeNet_habitat" ~ "Type of habitat homogenized across studies",
    Variable == "Bioregion" ~ "European biogiographical regions",
    Variable == "Country" ~ "Country where the plant-pollinator interaction was observed",
    Variable == "Locality" ~ "Locality where the plant-pollinator interaction was observed",
    Variable == "Latitude-Longitude" ~ "Coordinates of the observed interaction in decimal degrees",
    Variable == "Date" ~ "Year, month and day when the observation took place",
    Variable == "Interaction" ~ "Number of interactions. By default is 1 as interactions are provided ungrouped",
    Variable == "Plant_old_name" ~ "Plant species name given by the authors",
    Variable == "Plant_accepted_name" ~ "Harmonized plant species name in the database",
    Variable == "Plant_rank" ~ "Taxonomic rank of the observation",
    Variable == "Plant_order" ~ "Order taxonomic rank of the observed plant species",
    Variable == "Plant_family" ~ "Family taxonomic rank of the observed plant species",
    Variable == "Plant_genus" ~ "Genus taxonomic rank of the observed plant species",
    Variable == "Plant_unsure_id" ~ "Binary category to indicate if the plant species name is unsure (Yes) or not (No)",
    Variable == "Plant_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
    Variable == "Pollinator_old_name" ~ "Pollinator species name given by the authors",
    Variable == "Pollinator_accepted_name" ~ "Harmonized pollinator species name in the database",
    Variable == "Pollinator_rank" ~ "Taxonomic rank of the observation",
    Variable == "Pollinator_order" ~ "Order taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_family" ~ "Family taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_genus" ~ "Genus taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_unsure_id" ~ "Binary category to indicate if the pollinator species name is unsure (Yes) or not (No)",
    Variable == "Pollinator_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
    TRUE ~ "Other"
  ))

@@

# Results

@@

# Discussion

>>>>

---
title: "SafeNet: A European database of plant-pollinator interactions"
format:
  pdf:
    include-in-header: 
      text: |
        \usepackage{lscape}
        \newcommand{\blandscape}{\begin{landscape}}
        \newcommand{\elandscape}{\end{landscape}}
        \usepackage{caption}
        \captionsetup[figure]{labelformat=empty}
        \captionsetup[table]{labelformat=empty}

@@

#Prepare table with all info 
#Create variables
vars = colnames(safenet_database)
#Create table
d = tibble(Variable = vars)

#Add descriptor
my_tibble = d %>%
  mutate(Description = case_when(
    Variable == "Study_id" ~ "Identifier of the study",
    Variable == "Network_id" ~ "Identifier of a site sampled within a study",
    Variable == "Sampling_method" ~ "Type of plant-pollinator sampling",
    Variable == "Authors_habitat" ~ "Type of habitat as described by the authors",
    Variable == "SafeNet_habitat" ~ "Type of habitat homogenized across studies",
    Variable == "Bioregion" ~ "European biogiographical regions",
    Variable == "Country" ~ "Country where the plant-pollinator interaction was observed",
    Variable == "Locality" ~ "Locality where the plant-pollinator interaction was observed",
    Variable == "Latitude-Longitude" ~ "Coordinates of the observed interaction in decimal degrees (two columns)",
    Variable == "Date" ~ "Year, month and day when the observation took place",
    Variable == "Interaction" ~ "Number of interactions. By default is 1 as interactions are provided ungrouped",
    Variable == "Plant_old_name" ~ "Plant species name given by the authors",
    Variable == "Plant_accepted_name" ~ "Harmonized plant species name in the database",
    Variable == "Plant_rank" ~ "Taxonomic rank of the observation",
    Variable == "Plant_order" ~ "Order taxonomic rank of the observed plant species",
    Variable == "Plant_family" ~ "Family taxonomic rank of the observed plant species",
    Variable == "Plant_genus" ~ "Genus taxonomic rank of the observed plant species",
    Variable == "Plant_unsure_id" ~ "Binary category to indicate if the plant species name is unsure (Yes) or not (No)",
    Variable == "Plant_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
    Variable == "Pollinator_old_name" ~ "Pollinator species name given by the authors",
    Variable == "Pollinator_accepted_name" ~ "Harmonized pollinator species name in the database",
    Variable == "Pollinator_rank" ~ "Taxonomic rank of the observation",
    Variable == "Pollinator_order" ~ "Order taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_family" ~ "Family taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_genus" ~ "Genus taxonomic rank of the observed pollinator species",
    Variable == "Pollinator_unsure_id" ~ "Binary category to indicate if the pollinator species name is unsure (Yes) or not (No)",
    Variable == "Pollinator_uncertainty_type" ~ "If the name is unsure, type of species uncertainty is provided",
    TRUE ~ "Other"
  ))

@@

# 1 | INTRODUCTION

@@

# 2 | METHODS

@@

# Data structure

The SafeNet database is available in both .csv and .rds formats. The .csv file contains data in long format, while the .rds file stores the data in a list structure, with networks organized within each study. The data is organized in three different files named interaction data, flower count data and metadata. The interaction file contains `r nrow(my_tibble) + 1` columns that depict where and when the plant-pollinator interaction was observed (**Table 1**). To provide a standard unit of plant-pollinator interaction across studies, each row depicts a single interaction between a plant and a pollinator species. To build a plant-pollinator network matrix at a site level, authors only need to group interactions by plant and pollinator species, site and study. In addition, information about habitat type and bioclimatic region are also provided in this file. The floral count file contains measurements of floral availability and the unit of measurement, and should be merged with the interaction file by using the old plant name provided by the authors, site, and date if available. Only xxxx% of studies contain floral count information. The metadata file contains [...]

@@

@@

# 3 | RESULTS

@@

# 3 | DISCUSSION
